---
title: "RWorksheet_Ceniza#4a"
author: "Zydrick Ceniza"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Worksheet-4a in R
### Zydrick Ceniza BSIT-2B

## 1. The table below shows the data about shoe size and height. Create a data frame.
a. Describe the data.
The data imported choose the column shoes size and height 
```{r}
library(readxl)
Shoes <- read_excel("Shoes.xlsx")
Shoes[,1:2]
str(Shoes)
```

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
```{r}
subsetMale <- subset(Shoes,Gender == "M")
subsetMale
subsetFemale <- subset(Shoes,Gender == "F")
subsetFemale
```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
num1c<-factor
mean(Shoes$`Shoe size`)
mean(Shoes$Height)
```

d. Is there a relationship between shoe size and height? Why?
```{r, echo=False}
#Yes, there is a relationship between shoe size and height like the taller you are the bigger the shoes size
```

##2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
Consider data consisting of the names of months:
"March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September,"November","February",April")
```{r}
months_vector <- c("March", "April", "January", "November", "January","September", "October", "September", "November", "August","January", "November", "November", "February", "May", "August","July", "December", "August", "August", "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)

factor_months_vector
```

##3. Then check the summary() of the months_vector and factor_months_vector. | Inter-pret the results of both vectors. Are they both equally useful in this case?

```{r}
summary(months_vector)
summary(factor_months_vector)
#The result in summary of months_vector it just interpret the length, class, and mode of it and in the summary of factors_months_vectors it interpret how many number the months repeat itself in a vector.
```
The result in summary of months_vector it just interpret the length, class, and mode of it and in the summary of factors_months_vectors it interpret how many number the months repeat itself in a vector.

##4. Create a vector and factor for the table below.
```{r}
dir<-c("East","West","West","North","West","North","West","North")
num4<-data.frame(
  Direction=c("East","West","North"),
  Frequency=c(1,4,3)
)
num4
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```

##5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
```{r}
library(readr)
import_march <- read_csv("import_march.csv")
import_march
data <- read.table("import_march.csv", header = TRUE, sep = ",")
```

b. View the dataset. Write the R scripts and its result.
```{r}
View(import_march)
```

#Using Conditional Statements (IF-ELSE)

##6. Full Search
Exhaustive search is a methodology for finding an answer by exploring all possible cases.
When trying to find a desired number in a set of given numbers, the method of finding
the corresponding number by checking all elements in the set one by one can be called an
exhaustive search. Implement an exhaustive search function that meets the input/output
conditions below.
a. Create an R Program that allows the User to randomly select numbers from 1 to 50.
Then display the chosen number. If the number is beyond the range of the selected choice,
it will have to display a string “The number selected is beyond the range of 1 to 50”. If
number 20 is inputted by the User, it will have to display “TRUE”, otherwise display the
input number.

